Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-21 paper-2023-acsos-pulverization.tex
add a more detailed description of the implementation details of the framework. Please check @metaphori @danysk

>>>>

\meta{
The runtime bases its operation on three main components:
the \texttt{Spawner}, which is responsible for executing the components;
the \texttt{UnitReconfigurator}, which is responsible for reconfigure the \emph{deployment unit}
according to the \texttt{ReconfigurationEvent}
and the \texttt{Communicator}s which are used to establish the components' intra-communication.
%
To start, the \texttt{PulverisationRuntime} needs to know the name of the \emph{logical device},
the \emph{host} on which is running, and the configurations produced by the two \ac{dsl}s.
%
At the start of the system the runtime,
based on the provided configuration,
spawn all the components that must start on the \emph{deployment unit}.
%
Similarly, the \texttt{UnitReconfigurator} start observing all the configured \texttt{ReconfigurationEvent}s,
and register the listeners for incoming reconfigurations.
%
Each spawned component start to execute its logic and share data with other component via the \texttt{Communicator},
which is responsible for the components' intra-communication by leveraging the communication protocol.
%
When a reconfiguration occurs, the \texttt{UnitReconfigurator} takes into account the new deployment configuration
by interacting with the \texttt{Spawner} to start or stop the required components.
}
